Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Finish conclusions section

Deriving a quality score only from textual information and other non-structured data such as images is not trivial. 
However, in this study we managed to answer all seven research questions and find factors that can posittively or 
negatively affect the quality of a ticket.

In this study, we have answered all the research 
questions we set to answer and successfully proven that all of our results are statistically significant.

>>>>

Deriving a quality score only from textual information and other non-structured data such as images is not trivial. 
However, in this study we managed to create an application that can automatically fetch and store tickets from any 
Jira instance, analyse them and compute statistical tests and graphs.

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the quality of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce increases the quality of a ticket;
  \item the presence of stack traces increases the quality of a ticket;
  \item the presence of attachments increases the quality of a ticket - more specifically tickets with screenshots, 
  config files or text files have lower times-to-complete than tickets without attachments;
  \item higher numbers of grammar errors impply lower quality scores for a ticket;
  \item higher sentiment scores imply higher quality scores for a ticket;
  \item higher numbers of words in comments imply lower quality scores for a ticket;
  \item higher number of words in description and summary imply lower quality scores for a ticket.
\end{itemize}

We intend to continue work on the project and implement the points we have listed in Section \ref{future_work}. We believe
that by open sourcing the application and making the data publicly available, we can provide a valuable starting point 
for other studies investigating this particular field of software engineering.
